---
title: "Data"
---

Data of the project are Zip.csv and FamilyHome_Sales.csv (See introdution for more information)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(ggplot2)
library(lattice)
library(latexpdf)
Zipcode<- read.csv("Zipcode.csv")
FHS <- read.csv("FamilyHome_Sales.csv")
attach(Zipcode)
attach(FHS)
```

## Data Analysis 
The data analysis part contains two datasets using descriptive analysis, data visualization and more inferentialv statistical analyses


###Descriptive Analysis + Data visualization 

Since datasets are already loaded. The first step is to use the summary function to conclude the number of males and females in the zipcode file. 

Five-factor summary of the count of males
```{r}
summary(Zipcode$COUNT.MALE)
```
Five-factor summary of the count of females
```{r}
summary(Zipcode$COUNT.FEMALE)
```

Five-factor summary of the count of Asian, Non Hispanic
```{r}
summary(Zipcode$COUNT.ASIAN.NON.HISPANIC)
```
Five-factor summary of the count of Black, Non Hispanic
```{r}
summary(Zipcode$COUNT.BLACK.NON.HISPANIC)
```

-------------------------------------------------------------------------------------------------------------
Five-factor summary of Averagae Housing Sale Price in NYC (2009)
```{r}
summary(FHS$AVERAGE.SALE.PRICE)
```

Five-factor summary of Lowest Housing Sale Price in NYC (2009)
```{r}
summary(FHS$LOWEST.SALE.PRICE)
```

Five-factor summary of Highest Housing Sale Price in NYC (2009)
```{r}
summary(FHS$HIGHEST.SALE.PRICE)
```

Use ggplot to the distribution of totoal number of properties vs. number of sales in NYC (2009)
```{r}
p <- ggplot(FHS, aes(TOTAL.NO..OF.PROPERTIES,NUMBER.OF.SALES))
p + geom_point(colour = "red", size = 1.5)
```
Use ggplot to the distribution of lowest sale prices vs. type of home (2009)
```{r}
ggplot(FHS, aes(x = TYPE.OF.HOME, y = LOWEST.SALE.PRICE)) +
  geom_point(size = 2, shape = 23)
```
Use ggplot to the distribution of median sale prices vs. type of home (2009)
```{r}
ggplot(FHS, aes(x = TYPE.OF.HOME, y = MEDIAN.SALE.PRICE)) +
  geom_point(size = 2, shape = 20)
```
Use ggplot to the distribution of highest sale prices vs. type of home (2009)
```{r}
ggplot(FHS, aes(x = TYPE.OF.HOME, y = HIGHEST.SALE.PRICE)) +
  geom_point(size = 2, shape = 20)
```

Use ggplot to the distribution of average sale prices vs. type of home (2009)
```{r}
ggplot(FHS, aes(x = TYPE.OF.HOME, y = AVERAGE.SALE.PRICE)) +
  geom_point(size = 2, shape = 20)
```

-------------------------------------------------------------------------------------------------------------
Display the histogram of the percent of Asian
```{r}
hist(Zipcode$PERCENT.ASIAN.NON.HISPANIC, breaks = 6, col = "Blue")
```
Display the histogram of the percent of Black
```{r}
hist(Zipcode$PERCENT.BLACK.NON.HISPANIC, breaks = 6, col = "Blue")
```
Display the histogram of the percent of US Citizens
```{r}
hist(Zipcode$PERCENT.US.CITIZEN, breaks = 6, col = "Blue")
```
-------------------------------------------------------------------------------------------------------------

##Inferential Statistical Analyses 

###Correlation, Regression, t-test, Wilcox Test, ANOVA, Cumulative Distribution

Find the correlation between the number of female and male
```{r}
cor(Zipcode$COUNT.FEMALE,Zipcode$COUNT.MALE)
```

Conduct a regression analysis of the number of citizen and the number of males
```{r}
lm(Zipcode$COUNT.US.CITIZEN~Zipcode$COUNT.MALE)
```
Multiple Regression of percent of citizen total, percent of feamle, percent of pacific islander and percent of public assistance total
```{r}
lm(Zipcode$PERCENT.CITIZEN.STATUS.TOTAL~ Zipcode$PERCENT.FEMALE + Zipcode$PERCENT.PACIFIC.ISLANDER + Zipcode$PERCENT.PUBLIC.ASSISTANCE.TOTAL)
```
Conduct a two sample t-test of the number of American Indian and Asian Non Hispanic
```{r}
t.test(Zipcode$COUNT.AMERICAN.INDIAN,Zipcode$COUNT.ASIAN.NON.HISPANIC)
```
Conduct a two sample t-test of the number of black non hispanic and white non hispanic
```{r}
t.test(Zipcode$COUNT.BLACK.NON.HISPANIC, Zipcode$COUNT.WHITE.NON.HISPANIC)
```
Conduct a Rank sum test of the number of males and females 
```{r}
wilcox.test(Zipcode$COUNT.MALE, Zipcode$COUNT.FEMALE)
```
Conduct a rank sum test of the number of people who receives the public assistance and those people who do not receive
```{r}
wilcox.test(Zipcode$COUNT.RECEIVES.PUBLIC.ASSISTANCE, Zipcode$COUNT.NRECEIVES.PUBLIC.ASSISTANCE)
```
Find the difference between the number of people who receives the public assistance and those people who do not receive 
```{r}
DiffPubAssist <- setdiff(Zipcode$COUNT.RECEIVES.PUBLIC.ASSISTANCE, Zipcode$COUNT.NRECEIVES.PUBLIC.ASSISTANCE)
```

Conduct a sign test 
```{r}
wilcox.test(DiffPubAssist)
```
Conduct a ANOVA test using the percent of Asians and Americans
```{r}
aov(PERCENT.ASIAN.NON.HISPANIC ~ PERCENT.AMERICAN.INDIAN, data=Zipcode)
```

Cumulative distribution function of Count Participants
```{r}
pnorm(Zipcode$COUNT.PARTICIPANTS)
```
-------------------------------------------------------------------------------------------------------------
Conduct a rank sum testof houses with lowest sales price and highest sales price
```{r}
wilcox.test(FHS$LOWEST.SALE.PRICE, FHS$HIGHEST.SALE.PRICE)
```
Conduct a rank sum test of houses with lowest sales price and average sales price
```{r}
wilcox.test(FHS$AVERAGE.SALE.PRICE, FHS$LOWEST.SALE.PRICE)
```

Conduct a rank sum test of houses with highest sales price and average sales price
```{r}
wilcox.test(FHS$AVERAGE.SALE.PRICE, FHS$HIGHEST.SALE.PRICE)
```

Conduct a two sample t-test of houses with highest sales price and average sales price
```{r}
t.test(FHS$AVERAGE.SALE.PRICE,FHS$HIGHEST.SALE.PRICE)
```

Conduct a two sample t-test of houses with lowest sales price and average sales price
```{r}
t.test(FHS$AVERAGE.SALE.PRICE,FHS$LOWEST.SALE.PRICE)
```
